Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-03 prop.tex
prop.tex \section{Quantum IVPMs Whose Core has an Unique Element} Updating...

\section{Properties of Quantum IVPMs Decided by Their Range}

@@

\begin{lemma}Consider a regular collection of intervals~$\mathscr{I}$
with a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
Then, given a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$ defined by
$\bar{\mu}(P)=\iota\left(\mu(P)\right)$ is a quantum IVPM.\end{lemma}
\begin{proof}
~
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\iota\left(\mu(\mathbb{0})\right)=\iota\left(0\right)=\left[0,0\right]$.
\item $\bar{\mu}(\mathbb{1})=\iota\left(\mu(\mathbb{1})\right)=\iota\left(1\right)=\left[1,1\right]$. 
\item For any projection $P$, $\bar{\mu}\left(\mathbb{1}-P\right)=\iota\left(\mu(\mathbb{1}-P)\right)=\iota\left(1-\mu(P)\right)=\left[1,1\right]-\iota\left(\mu(P)\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have $\sum_{i=1}^{N}\mu\left(P_{i}\right)=\mu\left(\sum_{i=1}^{N}P_{i}\right)\in\left[0,1\right]$
so that $\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)=\iota\left(\mu\left(\sum_{i=1}^{N}P_{i}\right)\right)=\iota\left(\sum_{i=1}^{N}\mu\left(P_{i}\right)\right)\subseteq\sum_{i=1}^{N}\iota\left(\mu\left(P_{i}\right)\right)=\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$. 
\end{itemize}
\end{proof}
\begin{lemma}Consider regular a collection of intervals~$\mathscr{I}$
with a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
Then, there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that $\mathrm{core}\left(\bar{\mu}\right)$ has an unique element.\end{lemma}
\begin{proof}
Consider $\bar{\mu}(P)=\iota\left(\mu_{\ket{0}}^{B}(P)\right)$. Then,
$\bar{\mu}\left(\proj{0}\right)=\iota\left(\mu_{\ket{0}}^{B}\left(\proj{0}\right)\right)=\iota\left(1\right)=\left[1,1\right]$,
i.e., for any quantum probability measure~$\mu\in\mathrm{core}\left(\bar{\mu}\right)$,
we have $\mu\left(\proj{0}\right)=1$. Therefore, $\mu=\mu_{\ket{0}}^{B}$.
\end{proof}
\begin{example}For any positive odd integer~$n$, consider the collection
of intervals~$\mathscr{I}_{n}=\left\{ \left[0,0\right],\left[1,1\right]\right\} \cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}$,
and the map~$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
defined by 
\[
\iota_{n}\left(x\right)=\begin{cases}
\left[0,0\right] & \textrm{, if }x=0\textrm{ ;}\\
\left[\frac{k}{n},\frac{k+1}{n}\right] & \textrm{, if }\frac{k}{n}<x\le\frac{k+1}{n}<\frac{1}{2}\textrm{ ;}\\
\left[\frac{1}{2}-\frac{1}{2n},\frac{1}{2}+\frac{1}{2n}\right] & \textrm{, if }\frac{1}{2}-\frac{1}{2n}<x<\frac{1}{2}+\frac{1}{2n}\textrm{ ;}\\
\left[\frac{k}{n},\frac{k+1}{n}\right] & \textrm{, if }\frac{1}{2}<\frac{k}{n}\le x<\frac{k+1}{n}\textrm{ ;}\\
\left[1,1\right] & \textrm{, if }x=1\textrm{ .}
\end{cases}
\]
\end{example}
\begin{proof}
~
\begin{itemize}
\item $\iota\left(0\right)=\left[0,0\right]$.
\item $\iota\left(1\right)=\left[1,1\right]$. 
\item When $x=0$, $\iota\left(1-x\right)=\iota\left(1\right)=\left[1,1\right]=\left[1,1\right]-\iota\left(x\right)$.\\
When $\frac{k}{n}<x\le\frac{k+1}{n}<\frac{1}{2}$, we have $1-\frac{k}{n}>1-x\ge1-\frac{k+1}{n}>\frac{1}{2}$
so that $\iota\left(1-x\right)=\left[1-\frac{k+1}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\left[\frac{k}{n},\frac{k+1}{n}\right]=\left[1,1\right]-\iota\left(x\right)$.\\
When $\frac{1}{2}-\frac{1}{2n}<x<\frac{1}{2}+\frac{1}{2n}$, we have
$\frac{1}{2}+\frac{1}{2n}>1-x>\frac{1}{2}-\frac{1}{2n}$ so that $\iota\left(1-x\right)=\left[1-\frac{k+1}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\left[\frac{k}{n},\frac{k+1}{n}\right]=\left[1,1\right]-\iota\left(x\right)$.\\
The rest of the cases are true because of symmetry.
\item It is sufficient to prove the case when $N=2$, i.e., for a set $\left\{ x_{1},x_{2}\right\} \subseteq\left[0,1\right]$,
if $x_{1}+x_{2}\in\left[0,1\right]$, then $\iota\left(x_{1}+x_{2}\right)\subseteq\iota\left(x_{1}\right)+\iota\left(x_{2}\right)$.
\end{itemize}
\end{proof}

>>>>

\section{Quantum IVPMs Whose Core has an Unique Element}

@@

\begin{lemma}Consider a regular collection of intervals~$\mathscr{I}$
with a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
Then, given a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$ defined by
$\bar{\mu}(P)=\iota\left(\mu(P)\right)$ is a quantum IVPM.\end{lemma}
\begin{proof}
~
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\iota\left(\mu(\mathbb{0})\right)=\iota\left(0\right)=\left[0,0\right]$.
\item $\bar{\mu}(\mathbb{1})=\iota\left(\mu(\mathbb{1})\right)=\iota\left(1\right)=\left[1,1\right]$. 
\item For any projection $P$, $\bar{\mu}\left(\mathbb{1}-P\right)=\iota\left(\mu(\mathbb{1}-P)\right)=\iota\left(1-\mu(P)\right)=\left[1,1\right]-\iota\left(\mu(P)\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have $\sum_{i=1}^{N}\mu\left(P_{i}\right)=\mu\left(\sum_{i=1}^{N}P_{i}\right)\in\left[0,1\right]$
so that $\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)=\iota\left(\mu\left(\sum_{i=1}^{N}P_{i}\right)\right)=\iota\left(\sum_{i=1}^{N}\mu\left(P_{i}\right)\right)\subseteq\sum_{i=1}^{N}\iota\left(\mu\left(P_{i}\right)\right)=\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$. 
\end{itemize}
\end{proof}
\begin{lemma}Consider regular a collection of intervals~$\mathscr{I}$
with a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
Then, there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that $\mathrm{core}\left(\bar{\mu}\right)$ has an unique element.\end{lemma}
\begin{proof}
Consider $\bar{\mu}(P)=\iota\left(\mu_{\ket{0}}^{B}(P)\right)$. Then,
$\bar{\mu}\left(\proj{0}\right)=\iota\left(\mu_{\ket{0}}^{B}\left(\proj{0}\right)\right)=\iota\left(1\right)=\left[1,1\right]$,
i.e., for any quantum probability measure~$\mu\in\mathrm{core}\left(\bar{\mu}\right)$,
we have $\mu\left(\proj{0}\right)=1$. Therefore, $\mu=\mu_{\ket{0}}^{B}$.
\end{proof}
\begin{example}For any positive odd integer~$n$, the collection
of intervals~$\mathscr{I}_{n}=\set{\left[\frac{k}{n},\frac{k}{n}\right]}{k=0,\ldots,n}\cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}$,
and the map~$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
defined by 
\[
\iota_{n}\left(x\right)=\begin{cases}
\left[\frac{k}{n},\frac{k}{n}\right] & \textrm{, if }x=\frac{k}{n}\textrm{ ;}\\
\left[\frac{k}{n},\frac{k+1}{n}\right] & \textrm{, if }\frac{k}{n}<x<\frac{k+1}{n}\textrm{ .}
\end{cases}
\]
is regular.\end{example}
\begin{proof}
~
\begin{itemize}
\item $\iota\left(0\right)=\left[0,0\right]$.
\item $\iota\left(1\right)=\left[1,1\right]$. 
\item When $x=\frac{k}{n}$, we have $\iota\left(1-x\right)=\left[1-\frac{k}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\iota\left(x\right)$.\\
When $\frac{k}{n}<x<\frac{k+1}{n}$, we have $1-\frac{k}{n}>1-x>1-\frac{k+1}{n}$
so that $\iota\left(1-x\right)=\left[1-\frac{k+1}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\left[\frac{k}{n},\frac{k+1}{n}\right]=\left[1,1\right]-\iota\left(x\right)$.
\item It is sufficient to prove the case when $N=2$, i.e., for a set $\left\{ x_{1},x_{2}\right\} \subseteq\left[0,1\right]$,
if $x_{1}+x_{2}\in\left[0,1\right]$, then $\iota\left(x_{1}+x_{2}\right)\subseteq\iota\left(x_{1}\right)+\iota\left(x_{2}\right)$,
and the rest can be done by the induction. 
\begin{itemize}
\item When $x_{1}=\frac{k_{1}}{n}$, we have $\iota\left(x_{1}+x_{2}\right)=\left[\frac{k_{1}}{n},\frac{k_{1}}{n}\right]+\iota\left(x_{2}\right)=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)$.
\item When $\frac{k_{1}}{n}<x_{1}<\frac{k_{1}+1}{n}$ and $\frac{k_{2}}{n}<x_{2}<\frac{k_{2}+1}{n}$,
we have $\frac{k_{1}+k_{2}}{n}<x_{1}+x_{2}<\frac{k_{1}+k_{2}+2}{n}$
$\iota\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}+k_{2}}{n},\frac{k_{1}+k_{2}+2}{n}\right]=\left[\frac{k_{1}}{n},\frac{k_{1}+1}{n}\right]+\left[\frac{k_{2}}{n},\frac{k_{2}+1}{n}\right]=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)$.
\end{itemize}
\end{itemize}
\end{proof}
